ANNO: The Anthropological Notation Ontology

### 2023-04-06 paper.tex
Add GFO image and update core image.

For the foundation of the TO we used the \emph{General Formal Ontology} (GFO)~\citep{gfo} as TLO.
In the current paper, we refer especially to the categories \enquote{Material object}, \enquote{Property} as well as the spatial entities of GFO (Fig. …).
One of the advantages of the three-ontology method is that the software only needs to implement the access to entities (classes, properties) of the TO (ANNO-core),
whereas the entities of the corresponding DO (ANNO-domain) are processed dynamically.
\aw{} uses the ANNO-core as an interface to access the ANNO-domain entities (e.g., by listing all subclasses of a specific ANNO-core class).

@@

\section{Description of ANNO}

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{img/core.pdf}
\caption{ANNO-core ontology}\label{fig:core}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{img/gfo.pdf}
\caption{Integration of ANNO with the top-level GFO ontology.}\label{fig:gfo}
\end{figure}

For the foundation of the TO we used the \emph{General Formal Ontology} (GFO)~\citep{gfo} as TLO.
In the current paper, we refer especially to the categories \enquote{Material object}, \enquote{Property} as well as the spatial entities of GFO, see \cref{fig:gfo}.

One of the advantages of the three-ontology method is that the software only needs to implement the access to entities (classes, properties) of the TO (ANNO-core),
whereas the entities of the corresponding DO (ANNO-domain) are processed dynamically.
\aw{} uses the ANNO-core as an interface to access the ANNO-domain entities (e.g., by listing all subclasses of a specific ANNO-core class).

@@

\section{Description of ANNO}
\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{img/core.pdf}
\caption{ANNO-core ontology}\label{fig:core}
\end{figure}
